Master's Project Journal

### 2018-11-14 tex_files/Journal.tex
14-11-28

\section*{Phase Detection II}
The above phase detector was created using a state machine with the following diagram describing its behaviour:\\
%TODO insert image of the state transitions
It is preceded by two synchronisers which attempt to avoid metastable conditions, which will be used for the time being so that I could advance until we found a method that worked more generally.\\
I was able to test this phase detector and confirm that it was measuring a frequency difference in line with what I expected given my simulation results, despite spending too much time trying to figure out why the display was not giving me a reasonable output when it was just being updated far too quickly to be human readable.\\
%TODO insert image of the RTL diagram
I then realised I was also operating at a 160 MHz clock in both simulation and hardware so I attempted to push the clock up to the 400 MHz mark then but started to run into so timing issues on both inter and intra clock paths so I had to dial back the FPGA clock frequency to 258 MHz which was enough to remove all but what I think is an allowable timing violation on a synchroniser.\\
Working with the 1:0.1 rule for proportional/integral gains I then implemented a PI loop filter as in Eldar's PhD on Friday in order to complete an entire multi-bit ADPLL. After ironing out one issue caused by a lack of bit extension causing strange behaviour on the control code if it was negative which had gone undetected in simulation I was able to get my PLL locking to an on-chip reference signal late on Friday. In more detail the 8 bit signed output of the error loop filter was being added to a 12 bit bias signal and due to a lack of sign extension -1 became a +511. This error would correct itself on the next cycle leading to signal which looked like: $||--|||||-----||--|||||$\\%TODO do I have a screenshot of this error?
Pierre told me about his method for the arbiter so maybe I can implement that method myself rather than relying on my limited use case version.
%TODO insert a good simulation

>>>>

\section*{Phase Detection II}
The above phase detector was created using a state machine with the following diagram describing its behaviour:\\
%TODO insert image of the state transitions
It is preceded by two synchronisers which attempt to avoid metastable conditions, which will be used for the time being so that I could advance until we found a method that worked more generally.\\
I was able to test this phase detector and confirm that it was measuring a frequency difference in line with what I expected given my simulation results, despite spending too much time trying to figure out why the display was not giving me a reasonable output when it was just being updated far too quickly to be human readable.\\
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.33]{../ADPLL_RTL_VIVADO}
    \caption{RTL Diagram of the ADPLL}
    \label{fig:adpll_rtl}
\end{figure}
I then realised I was also operating at a 160 MHz clock in both simulation and hardware so I attempted to push the clock up to the 400 MHz mark then but started to run into so timing issues on both inter and intra clock paths so I had to dial back the FPGA clock frequency to 258 MHz which was enough to remove all but what I think is an allowable timing violation on a synchroniser.\\
Working with the 1:0.1 rule for proportional/integral gains I then implemented a PI loop filter as in Eldar's PhD on Friday in order to complete an entire multi-bit ADPLL.
After ironing out one issue caused by a lack of bit extension causing strange behaviour on the control code if it was negative which had gone undetected in simulation I was able to get my PLL locking to an on-chip reference signal late on Friday.
In more detail the 8 bit signed output of the error loop filter was being added to a 12 bit bias signal and due to a lack of sign extension -1 became a +511. This error would correct itself on the next cycle leading to signal which looked like: $||--|||||-----||--|||||$\\r
Pierre told me about his method for the arbiter so maybe I can implement that method myself rather than relying on my limited use case version.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.33]{../good_sim}
    \caption{Example simulation}
    \label{fig:example_sim}
\end{figure}

\section*{Basic Measurements}
Lock range at bias of 82:
$$4.19\rightarrow12.34\textrm{ MHz} $$ 
Capture range at bias of 82:
$$4.25\rightarrow12.76\textrm{ MHz}  $$
Jitter at bias of 82:\\
%TODO
Jitter locked to 5~ MHz:\\
%TODO
Frequency sensitivity(control code to output):
$$ 258\times10^6\frac{1}{2^{12}}=62.988\textrm{ MHz} $$
Overall proportional gain (time $\rightarrow$ TDC $\rightarrow$ frequency):
$$ 8.998 \textrm{ KHz/degree} $$
LPF cutoff:\\

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.33]{../HMO_locking_4M7_to5M0}
    \caption{Example of locking at startup}
    \label{fig:hmo_locking}
\end{figure}%redo on good scope
